---
title             : "Protection Motivation Theory Seasonal Influenza Vaccine"
shorttitle        : "PMT - Flu vax"

author: 
  - name          : "Mathew Ling"
    affiliation   : "1"
    corresponding : yes    
    address       : "Deakin University Locked Bag 20000"
    email         : "m.ling@deakin.edu.au"
  - name          : "Emily J. Kothe"
    affiliation   : "1"
  - name          : "Barbara A. Mullan"
    affiliation   : "2"  

affiliation:
  - id            : "1"
    institution   : "Deakin University, Geelong, Australia, Misinformation Lab, School of Psychology"
  - id            : "2"
    institution   : "Health Psychology and Behavioural Medicine Research Group, School of Psychology and Speech Pathology, Curtin University, Perth, Australia"


author_note: |
  
  Mathew Ling, Misinformation Lab, School of Psychology, Deakin University, Australia; Emily J. Kothe, Misinformation Lab, School of Psychology, Deakin University, Australia; Barbara A. Mullan, Health Psychology and Behavioural Medicine Research Group, School of Psychology and Speech Pathology, Curtin University, Perth, Australia.
  
  This research was supported in part by the Deakin University's Health ResAarch Capacity Building Grant ScHeme (HAtCH).  

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "Protection Motivation Theory, Immunisation, Seasonal Influenza"
wordcount         : "X"

bibliography      : ["r-references.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
library("papaja")
library(knitr)
library(readr)
library(dplyr)
library(broom)
```

```{r setglobal, cache = FALSE, include = TRUE}

opts_knit$set(root.dir = "..")

options(knitr.kable.NA = '')
```

```{r}
dat <- read_rds("./data/dat.rds")

flu <- dat %>% 
  filter(study=="Flu vaccination")
```



# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

Participants were recruited via Amazon MTurk. See Table \@ref(tab:demo) for a summary of participant characteristics. After data cleaning, `r nrow(flu)` participants were included in this study.

```{r demo, results='asis', warning=FALSE}
## flu_demo.csv is generated by create_tables.R

tab <- read_csv("manuscripts/flu_demo.csv")

names(tab)[1] <- "Demographic Characteristic"

Variables<-as.list(c(4:10, 12:19, 21:33))

papaja::apa_table(tab, caption="Demographic characteristics by study", stub_indents= Variables, longtable = TRUE)
```

## Material

## Procedure

## Data analysis
We used `r cite_r("manuscripts/r-references.bib")` for all our analyses.


# Results

```{r severity_int}

test <-  filter(flu, condition =="Control" | condition == "Severity")
t_out <- t.test(test$flu_int ~ as.factor(test$condition))

sev_tidy<-tidy(t_out)

sev<-apa_print(t_out)

```

```{r susceptibility_int}

test <-  filter(flu, condition =="Control" | condition == "Susceptibility")
t_out <- t.test(test$flu_int ~ as.factor(test$condition))

sus_tidy<-tidy(t_out)

sus<-apa_print(t_out)

```

```{r mrr_int}

test <-  filter(flu, condition =="Control" | condition == "Maladpative Response Rewards")
t_out <- t.test(test$flu_int ~ as.factor(test$condition))

mrr_tidy<-tidy(t_out)

mrr<-apa_print(t_out)

```

```{r se_int}

test <-  filter(flu, condition =="Control" | condition == "Self-Efficacy")
t_out <- t.test(test$flu_int ~ as.factor(test$condition))

se_tidy<-tidy(t_out)

se<-apa_print(t_out)

```

```{r re_int}

test <-  filter(flu, condition =="Control" | condition == "Response Efficacy")
t_out <- t.test(test$flu_int ~ as.factor(test$condition))

re_tidy<-tidy(t_out)

re<-apa_print(t_out)

```

```{r rc_int}

test <-  filter(flu, condition =="Control" | condition == "Response Costs")
t_out <- t.test(test$flu_int ~ as.factor(test$condition))

rc_tidy<-tidy(t_out)

rc<-apa_print(t_out)

```

A series of t-tests (see Table \@ref(tab:int)) were conducted to investigate the impact of each message on intention to vaccinate relative control. Messages were not effective at increasing intention to vaccinate (Severity: `r sev$statistic`; Susceptibility: `r sus$statistic`; MRR: `r mrr$statistic`; Self-efficacy: `r se$statistic`; Response Efficacy (`r re$statistic`); Response Costs: `r rc$statistic`).

```{r int, results="asis"}
int_tidy<-rbind(sev_tidy, sus_tidy, mrr_tidy, se_tidy, re_tidy, rc_tidy)

int_tidy$comparisons <- c("Severity vs. Control", "Susceptibility vs. Control", "MRR vs. Control", "Self-efficacy vs. Control", "Response Efficacy vs. Control", "Response Costs vs. Control")

int_tidy <- int_tidy %>% 
  select(comparisons, estimate1, estimate2, statistic, p.value)

apa_table(int_tidy, caption = "Impact of interventions on intention to vaccinate", placement = "htb")
```




```{r severity_coi}

test <-  filter(flu, condition =="Control" | condition == "Severity")
t_out <- t.test(test$flu_sev ~ as.factor(test$condition))

sev_tidy<-tidy(t_out)

sev<-apa_print(t_out)

```

```{r susceptibility_coi}

test <-  filter(flu, condition =="Control" | condition == "Susceptibility")
t_out <- t.test(test$flu_sus ~ as.factor(test$condition))

sus_tidy<-tidy(t_out)

sus<-apa_print(t_out)

```

```{r mrr_coi}

test <-  filter(flu, condition =="Control" | condition == "Maladpative Response Rewards")
t_out <- t.test(test$flu_mrr ~ as.factor(test$condition))

mrr_tidy<-tidy(t_out)

mrr<-apa_print(t_out)

```

```{r se_coi}

test <-  filter(flu, condition =="Control" | condition == "Self-Efficacy")
t_out <- t.test(test$flu_se ~ as.factor(test$condition))

se_tidy<-tidy(t_out)

se<-apa_print(t_out)

```

```{r re_coi}

test <-  filter(flu, condition =="Control" | condition == "Response Efficacy")
t_out <- t.test(test$flu_re ~ as.factor(test$condition))

re_tidy<-tidy(t_out)

re<-apa_print(t_out)

```

```{r rc_coi}

test <-  filter(flu, condition =="Control" | condition == "Response Costs")
t_out <- t.test(test$flu_rc ~ as.factor(test$condition))

rc_tidy<-tidy(t_out)

rc<-apa_print(t_out)

```

```{r coi, results="asis"}
coi_tidy<-rbind(sev_tidy, sus_tidy, mrr_tidy, se_tidy, re_tidy, rc_tidy)

#int_tidy<-cbind(c("Severity vs. Control", "Susceptibility vs. Control", "MRR vs. Control", "Self-efficacy vs. Control", "Response Efficacy vs. Control", "Response Costs vs. Control"), int_tidy)

coi_tidy$comparisons <- c("Severity vs. Control", "Susceptibility vs. Control", "MRR vs. Control", "Self-efficacy vs. Control", "Response Efficacy vs. Control", "Response Costs vs. Control")

coi_tidy$construct <- c("Severity", "Susceptibility", "MRR", "Self-efficacy", "Response Efficacy", "Response Costs")

coi_tidy <- coi_tidy %>% 
  select(comparisons, construct, estimate1, estimate2, statistic, p.value)

apa_table(coi_tidy, caption = "Impact of interventions on target construct", placement = "htb")
```


T-tests were also conducted to investigate the impact of each message on the PMT construct it was designed to target (i.e. the effect of the *self-efficacy* message on *self-efficacy*) relative to control. As shown in Table \@ref(tab:coi), although the the messages were generally not effective at bringing about changes in beliefs they were designed to target.

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
