---
title             : "Protection Motivation Theory Seasonal Influenza Vaccine"
shorttitle        : "PMT - Flu vax"

author: 
  - name          : "Mathew Ling"
    affiliation   : "1"
    corresponding : yes    
    address       : "Deakin University Locked Bag 20000"
    email         : "m.ling@deakin.edu.au"
  - name          : "Emily J. Kothe"
    affiliation   : "1"
  - name          : "Barbara A. Mullan"
    affiliation   : "2"  

affiliation:
  - id            : "1"
    institution   : "Deakin University, Geelong, Australia, Misinformation Lab, School of Psychology"
  - id            : "2"
    institution   : "Health Psychology and Behavioural Medicine Research Group, School of Psychology and Speech Pathology, Curtin University, Perth, Australia"


author_note: |
  
  Mathew Ling, Misinformation Lab, School of Psychology, Deakin University, Australia; Emily J. Kothe, Misinformation Lab, School of Psychology, Deakin University, Australia; Barbara A. Mullan, Health Psychology and Behavioural Medicine Research Group, School of Psychology and Speech Pathology, Curtin University, Perth, Australia.
  
  This research was supported in part by the Deakin University's Health ResAarch Capacity Building Grant ScHeme (HAtCH).  

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "Protection Motivation Theory, Immunisation, Seasonal Influenza"
wordcount         : "X"

bibliography      : ["../manuscripts/r-references.bib", "../manuscripts/refs.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no

class             : "man"
output            : papaja::apa6_pdf

header-includes:
  - \raggedbottom
---

```{r load_packages, include = FALSE}
library("papaja")
library(knitr)
library(readr)
library(dplyr)
library(broom)
library(here)
library(ggplot2)
library(cowplot)
```

```{r setglobal, cache = FALSE, include = TRUE}

opts_knit$set(root.dir = "..")

options(knitr.kable.NA = '')
```

```{r}
dat <- read_rds(here("data", "dat.rds"))

flu <- dat %>% 
  filter(study=="Flu vaccination")
```



# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->This study was pre-registered using a template for pre-registration of studies within social psychology [@van2016pre]. The pre-registration for this project is available at: [https://osf.io/nhcfv/](https://osf.io/nhcfv/).

## Participants

Participants were recruited to take part in a study on "Short study of responses to messages about scientific issues" in exchange for $1.10USD in Amazon credit via Amazon MTurk.  Sample size was determined *a priori*. We aimed to recruit a minimum of 526 participants per cell in order to detect an effect of d =.2, with 80% power, and an alpha of 0.0083. To account for missingness, we over-sampled each cell by 20, leading to recruitment target of 546 per condition. After removal of duplicate and incomplete submissions\footnote{Complete removal of data from participants with duplicate submissions was required in order to avoid contamination between conditions. Removal of incomplete submissions was required because submission of the completed survey indicated consent}, `r printnum(nrow(flu))` participants were included in this study. The final number of participants in each condition is shown in Table \@ref(tab:cond).

```{r cond, results="asis"}

cond <- as.data.frame(table(flu$condition))

apa_table(cond, 
          caption = "Final N per Condition", 
          placement = "htb", 
          col.names=c("Condition", "N"), 
          note = "MRR = Maladaptive Response Rewards")
```

```{r demo, results='asis', warning=FALSE}
## flu_demo.csv is generated by create_tables.R

tab <- read_csv(here("manuscripts", "flu_demo.csv"))

names(tab)[1] <- "Demographic Characteristic"

Variables<-as.list(c(4:10, 12:19, 21:33))

papaja::apa_table(tab, caption="Demographic characteristics of participants", stub_indents= Variables, longtable = TRUE)
```

## Material

## Procedure

Participants completed an online questionnaire that included all measures and the experimental manipulation via the online survey platform Qualtrics.

The first component of the questionnaire included measures of demographic variables (e.g. age, gender, household income). Participants were then randomly allocated (by Qualtrics) to one of the six intervention groups or control. Individuals allocated to receive an intervention message were  shown a message related instruction and then the target message.  Individuals in the control group did not receive the instruction or any message and instead proceeded directly to next part of the survey. Participants were not notified of their condition (or their allocation to a no message condition). In the third part of the questionnaire, participants completed the PMT questionnaire. The order of items within the PMT questionnaire was randomised to reduce order effects. At the conclusion of the study participants were invited to provided feedback on the survey via a free-text response box.

Data for this project was collected concurrently with data for a second project (described at [http://osf.io/2trbk](http://osf.io/2trbk)) in the following manner: 

- A single study listing both both studies was created on Amazon MTurk
- Interested participants read a Plain Language Statement that is relevant to both studies
- Consenting participants were sent to a single Qualtrics survey that contained the materials for both projects
- The randomisation feature within Qualtrics randomised participants to entry into either this project or the concurrent project
- Participants in this project were shown a message about seasonal flu vaccination and answered questions to relating to their vaccination beliefs
- Participants in the concurrent project were shown a message about climate change and answered questions relating to their climate change beliefs

Data collection for the two projects were administered in this manner in order to ensure that the samples are not contaminated (i.e. do not contain the same participants) as although the projects were not intended to be analysed or reported together, their structural similarity could cause unexpected effects for participants who participated in both (e.g. by resulting in unblinding). This method of data collection and the intention to analyse and report the studies separately was documented in the pre-registration for both studies.

## Messages

Participants were randomised to receive one of six intervention messages or to a no message control group. Each intervention message was designed to target a single PMT construct.\footnote{A set of 24 candidate messages (4 per PMT construct) were first developed by EJK and ML and reviewed by BAM. These messages were then tested in a pilot study with a convenience sample of X Australian adults. Participants in the pilot study viewed a single candidate message relating to flu or flu vaccination and responded to a single item measure related to the construct the measure was intended to target (e.g. a severity message and a single item measure of severity). The mean response was calculated for each candidate message, the candidate message with the largest (or smallest in the case of MRR and RC) mean value on the construct measure was chosen for use within this study.}  

- *"Flu season is starting soon. The flu is a serious lung infection that attacks millions of people every year. The flu can kill you. In the 2015-2016 flu season, an estimated 56,000 Americans died because of the flu."* - Severity
- "*Flu season is starting soon. It is estimated that 1 in 5 people get the flu each year. Because the types of flu circulating in the community change from year to year, you're at risk from the flu even if you got vaccinated last year.*" - Susceptibility
- *"Flu season is starting soon. Some people think that a benefit of not getting vaccinated is that getting the flu would mean time off work. But most people who get the flu feel horrible. The flu usually comes on suddenly and people have high fevers, severe headaches, extreme tiredness, a dry cough, and bad muscle aches. Often, people can't even get out of bed."* - Maladaptive Response Rewards
- *"Flu season is starting soon. It's easy to obtain a flu vaccine this season. You can get a vaccination from your doctor or pharmacist."* - Self-efficacy
- *"Flu season is starting soon. The flu vaccine is effective in protecting you during flu season. Even if you get the flu after having had the flu vaccine, your symptoms won't be as bad as if you hadn't been vaccinated."* - Response Efficacy
- *"Flu season is starting soon. Some people don't get the flu vaccine because they are worried about pain from the injection. But people with the flu have high fevers, severe headaches, extreme tiredness, a dry cough, and bad muscle ache meaning that the pain of the vaccine is much less than the pain of the flu."* - Response Costs

## Measures

### Demographics

Participants completed a short demographic questionnaire at the beginning of the study. This included items regarding age, gender, highest level of education completed, annual household income, and political ideology. 

Political ideology was measured using three ideological self-placement items. Participants were asked to indicate "When it comes to ... would you consider yourself" with reference to "politics in general", "economic issues" and "social issues". Each item was measured on a 0-10 point scale (0 = "Very Liberal": 10 = "Very Conservative").

### Intention

Intention was measured as the mean of three items (1= Strongly Disagree, 5 = Strongly Agree) regarding intention to engage in the referent behaviour "have a flu vaccination in the next flu season". Higher scores indicate greater intention to have the vaccination. 

### Severity

Participants indicated rated their agreement (from 1 = Strongly Disagree to 5 = Strongly Agree) with three items that indicated that the negative impact of flu is severe. The three items were averaged to create a composite score. Higher scores indicate greater perceived severity of seasonal influenza. 

### Susceptibility

Participants indicated rated their agreement (from 1 = Strongly Disagree to 5 = Strongly Agree) with two items that indicated that without a flu vaccination they are vulnerable to the negative impacts of seasonal influenza and one item indicating that without a flu vaccination they are not likely to get the flu. Items were reversed as appropriate and the three items were averaged to create a composite score. Higher scores indicate greater perceived susceptibility to negative impacts of influenza. 

### Maladaptive Response Rewards

Participants indicated rated their agreement (from 1 = Strongly Disagree to 5 = Strongly Agree) with three items that indicated that there are benefits of not receiving a flu vaccination. The three items were averaged to create a composite score. Higher scores indicate greater perceived maladaptive response rewards.

### Self-Efficacy

Participants indicated rated their agreement (from 1 = Strongly Disagree to 5 = Strongly Agree) with two items that indicated that they would be capable of engaging in the referent behaviour if they wished to do so, and one item that indicated that it would be difficult for them to get a flu vaccination. Items were reversed as appropriate and the three items were averaged to create a composite score. Higher scores indicate greater self-efficacy.

### Response Efficacy

Participants indicated rated their agreement (from 1 = Strongly Disagree to 5 = Strongly Agree) with three items that indicated that receiving a flu vaccine would be effective in reducing vulnerability and severity of seasonal flu. The three items were averaged to create a composite score. Higher scores indicate greater perceived response efficacy.

### Response Costs

Participants indicated rated their agreement (from 1 = Strongly Disagree to 5 = Strongly Agree) with three items that indicated that there are costs (including non-financial costs) associated with receiving a flu vaccination. The three items were averaged to create a composite score. Higher scores indicate greater perceived response costs.

## Data analysis
We used `r cite_r("manuscripts/r-references.bib")` for all our analyses. All t-tests were conducted using Welch's t-test. The alpha for the study was $\alpha$ = 0.0083.


# Results

## Pre-registered analyses
```{r intention_tests}

## Conduct a bunch of t-tests looking at the effect of messages on intention

## Intention by Severity
t_out     <- t.test(flu_int ~ as.factor(condition), 
                data = filter(flu, condition =="Control" | condition == "Severity"))
sev_tidy  <- tidy(t_out)
sev       <- apa_print(t_out)

## Intention by Susceptibility
t_out <- t.test(flu_int ~ as.factor(condition), 
                data=filter(flu, condition =="Control" | condition == "Susceptibility"))
sus_tidy<-tidy(t_out)
sus<-apa_print(t_out)

## Intention by MRR
t_out    <- t.test(flu_int ~ as.factor(condition), 
                data = filter(flu, condition =="Control" | condition == "MRR"))
mrr_tidy <- tidy(t_out)
mrr      <- apa_print(t_out)

## Intention by Self-Efficacy
t_out   <- t.test(flu_int ~ as.factor(condition),
                data = filter(flu, condition =="Control" | condition == "Self-Efficacy"))
se_tidy <- tidy(t_out)
se      <- apa_print(t_out)

## Intention by Response Efficacy
t_out   <- t.test(flu_int ~ as.factor(condition), 
                data = filter(flu, condition =="Control" | condition == "Response Efficacy"))
re_tidy <- tidy(t_out)
re      <- apa_print(t_out)

# Intention by Response Costs
t_out   <- t.test(flu_int ~ as.factor(condition), 
                filter(flu, condition =="Control" | condition == "Response Costs"))
rc_tidy <- tidy(t_out)
rc      <- apa_print(t_out)

```

```{r int, results="asis"}

## This section makes a table based on the t-tests in the previous chunk

int_tidy <- rbind(sev_tidy, sus_tidy, mrr_tidy, se_tidy, re_tidy, rc_tidy)

int_tidy$comparisons <- c("Control vs. Severity", 
                          "Control vs. Susceptibility", 
                          "Control vs. MRR", 
                          "Control vs. Self-efficacy", 
                          "Control vs. Response Efficacy", 
                          "Control vs. Response Costs")

int_tidy$p.value <- printp(int_tidy$p.value)

int_tidy <- int_tidy %>% 
  select(comparisons, estimate1, estimate2, statistic, p.value)

apa_table(int_tidy, 
          caption = "Impact of interventions on intention to recieve a flu vaccination relative to control", 
          placement = "htb", 
          col.names=c("Comparisions", "Control Mean", "Intervention Mean", "\\textit{t}", "\\textit{p}"), 
          align="lcccc", 
          note = "MRR = Maladaptive Response Rewards")
```

```{r intfig, fig.height=10, fig.cap="Intention to Vaccinate by Message", warning=FALSE}

## Create set of figures

ggplot(flu, aes(condition, flu_int)) + geom_boxplot() + theme_apa() + coord_flip() + labs(x = "", y = "Intention")
```

Summary statistics for each message on the intention measure are summarised in Figure \@ref(fig:intfig). A series of t-tests (see Table \@ref(tab:int)) were conducted to investigate the impact of each message on intention to vaccinate relative control. Messages were not effective at increasing intention to vaccinate (Severity: `r sev$statistic`; Susceptibility: `r sus$statistic`; MRR: `r mrr$statistic`; Self-efficacy: `r se$statistic`; Response Efficacy (`r re$statistic`); Response Costs: `r rc$statistic`).

```{r coi_tests}

## Conduct a bunch of t-tests looking at the effect of messages on the construct they are intended to target

t_out    <- t.test(flu_sev ~ as.factor(condition), data = filter(flu, condition =="Control" | condition == "Severity"))
sev_tidy <- tidy(t_out)
sev      <- apa_print(t_out)

t_out    <- t.test(flu_sus ~ as.factor(condition), data = filter(flu, condition =="Control" | condition == "Susceptibility"))
sus_tidy <- tidy(t_out)
sus      <- apa_print(t_out)

t_out    <- t.test(flu_mrr ~ as.factor(condition), filter(flu, condition =="Control" | condition == "MRR"))
mrr_tidy <- tidy(t_out)
mrr      <- apa_print(t_out)

t_out   <- t.test(flu_se ~ as.factor(condition), filter(flu, condition =="Control" | condition == "Self-Efficacy"))
se_tidy <- tidy(t_out)
se      <- apa_print(t_out)

t_out   <- t.test(flu_re ~ as.factor(condition), filter(flu, condition =="Control" | condition == "Response Efficacy"))
re_tidy <- tidy(t_out)
re      <- apa_print(t_out)

t_out   <- t.test(flu_rc ~ as.factor(condition), filter(flu, condition =="Control" | condition == "Response Costs"))
rc_tidy <- tidy(t_out)
rc      <- apa_print(t_out)

```

```{r coi, results="asis"}

## This section makes a table based on the t-tests in the previous chunk

coi_tidy<-rbind(sev_tidy, sus_tidy, mrr_tidy, se_tidy, re_tidy, rc_tidy)

coi_tidy$comparisons <- c("Control vs. Severity", 
                          "Control vs. Susceptibility", 
                          "Control vs. MRR", 
                          "Control vs. Self-efficacy", 
                          "Control vs. Response Efficacy", 
                          "Control vs. Response Costs")

coi_tidy$construct <- c("Severity", "Susceptibility", "MRR", "Self-efficacy", "Response Efficacy", "Response Costs")

coi_tidy <- coi_tidy %>% 
  select(comparisons, construct, estimate1, estimate2, statistic, p.value) %>% 
  mutate(p.value = printp(p.value))

apa_table(coi_tidy, 
          caption = "Impact of interventions on target construct relative to control", 
          placement = "htb", 
          col.names=c("Comparisions", "Construct", "Control Mean", "Intervention Mean", "\\textit{t}", "\\textit{p}"), 
          align="lcccc", small=TRUE,
          note = "MRR = Maladaptive Response Rewards")
```

```{r fig.height=10, fig.cap="Message vs. Control by Target Construct and Message", warning=FALSE}

## Create set of figures

sevplot <- ggplot(filter(flu, condition =="Control" | condition == "Severity"), aes(condition, flu_sev)) +  
              geom_boxplot() + theme_apa() + labs(x = "Message", y = "Severity Score")

susplot <- ggplot(filter(flu, condition =="Control" | condition == "Susceptibility"), aes(condition, flu_sus)) +
              geom_boxplot() + theme_apa() + labs(x = "Message", y = "Susceptibility Score")

mrrplot <- ggplot(filter(flu, condition =="Control" | condition == "MRR"), aes(condition, flu_mrr)) + 
              geom_boxplot() + theme_apa()  + labs(x = "Message", y = "MRR Score")

seplot <- ggplot(filter(flu, condition =="Control" | condition == "Self-Efficacy"), aes(condition, flu_se)) + 
              geom_boxplot() + theme_apa() + labs(x = "Message", y = "Self-Efficacy Score")

replot <- ggplot(filter(flu, condition =="Control" | condition == "Response Efficacy"), aes(condition, flu_re)) + 
              geom_boxplot() + theme_apa()  + labs(x = "Message", y = "Response Efficacy Score")

rcplot <- ggplot(filter(flu, condition =="Control" | condition == "Response Costs"), aes(condition, flu_rc)) + 
              geom_boxplot() + theme_apa() + labs(x = "Message", y = "Response Costs Score")

plot_grid(sevplot, susplot, mrrplot, seplot, replot, rcplot, ncol=2, labels = c("A", "B", "C", "D", "E", "F"))
```

T-tests were also conducted to investigate the impact of each message on the PMT construct it was designed to target (i.e. the effect of the *self-efficacy* message on *self-efficacy*) relative to control. As shown in Table \@ref(tab:coi), although the the messages were generally not effective at bringing about changes in beliefs they were designed to target. However, individuals in the Severity message group did report significantly higher perceived severity of the flu than control participants `r sev$statistic`. 

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
