---
title             : "Protection Motivation Theory Climate Change Denial"
shorttitle        : "PMT - CCD"

author: 
  - name          : "Emily J. Kothe"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Deakin University Locked Bag 20000"
    email         : "emily.kothe@deakin.edu.au"
  - name          : "Mathew Ling"
    affiliation   : "1"
  - name          : "Barbara A. Mullan"
    affiliation   : "2"  

affiliation:
  - id            : "1"
    institution   : "Deakin University, Geelong, Australia, Misinformation Lab, School of Psychology"
  - id            : "2"
    institution   : "Health Psychology and Behavioural Medicine Research Group, School of Psychology and Speech Pathology, Curtin University, Perth, Australia"
    
author_note: |
  Emily J. Kothe, Misinformation Lab, School of Psychology, Deakin University, Australia; Mathew Ling, Misinformation Lab, School of Psychology, Deakin University, Australia; Barbara A. Mullan, Health Psychology and Behavioural Medicine Research Group, School of Psychology and Speech Pathology, Curtin University, Perth, Australia.
  
  This research was supported in part by the Deakin University's Health ResAarch Capacity Building Grant ScHeme (HAtCH).  
  
abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "Protection Motivation Theory, Climate Change, Sustainability"
wordcount         : "X"

bibliography      : ["../manuscripts/r-references.bib", "../manuscripts/refs.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
library("papaja")
library(knitr)
library(readr)
library(dplyr)
library(broom)
library(here)
library(ggplot2)
library(cowplot)
```

```{r setglobal, cache = FALSE, include = TRUE}

opts_knit$set(root.dir = "..")

options(knitr.kable.NA = '')
```

```{r}
dat <- read_rds(here("data", "dat.rds"))

climate <- dat %>% 
  filter(study=="Climate Change")
```


# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) --> This study was pre-registered using the template for pre-registration in social psychology developed by @van2016pre. The pre-registration for this project is available at: [https://osf.io/2g6bq/](https://osf.io/2g6bq/).

## Participants

Participants were recruited via Amazon MTurk to take part in a study on "Short study of responses to messages about scientific issues" in exchange for $1.10USD in Amazon credit.  Sample size was determined *a priori*, we aimed to recruit a minimum of 526 participants per cell in order to detect an effect of d =.2, with 80% power, and an alpha of 0.0083. To account for missingness, we oversampled each cell by 20, leading to recruitment target of 546 per condition and a total recruitment target of 3822. After removal of duplicate and incomplete submissions\footnote{Complete removal of data from participants with duplicate submissions was required in order to avoid contamination between conditions. Removal of incomplete submissions was required because submission of the completed survey indicated consent}, `r printnum(nrow(climate))` participants were included in this study. The final number of participants in each condition is shown in Table \@ref(tab:cond).

```{r cond, results="asis"}

cond <- as.data.frame(table(climate$condition))

apa_table(cond, caption = "Final N per Condition", placement = "htb", col.names=c("Condition", "N"))

```

Three participants reported an age value that was not plausible (i.e. below the allowed age for registration on MTurk or above 200 years). These ages were converted to missing but the responses of those participants were otherwise retained. Gender was recorded using a free-text field and then categorised manually, Four participants provided a response to this item that could not be meaningfully catergorised (in all cases these representated responses that did not appear to reflect gender identity e.g. "%" or "40"). These responses were converted to missing but the responses of those participants were otherwise retained. See Table \@ref(tab:demo) for a summary of participant characteristics. 

```{r demo, results='asis', warning=FALSE}
## climate_demo.csv is generated by create_tables.R

tab <- read_csv(here("manuscripts", "climate_demo.csv"))

names(tab)[1] <- "Demographic Characteristic"

Variables<-as.list(c(4:10, 12:19, 21:33))

papaja::apa_table(tab, caption="Demographic characteristics of participants", stub_indents = Variables, longtable = TRUE)
```

## Procedure

The study was administered via the online survey platform Qualtrics. Participants who chose to take part in the study completed an online questionnaire that included all measures and the experimental manipulation.

The first component of the questionnaire included measures of demographic variables (e.g. age, gender, household income). Participants were then randomly allocated (by Qualtrics) to one of the six intervention groups or control. Individuals allocated to receive an intervention message were  shown a message related instruction and then the target message.  Individuals in the control group did not receive the instruction or any message and instead proceeded directly to next part of the survey. Participants were not notified of their condition (or their allocation to a no message condition). In the third part of the questionnaire, participants completed the PMT questionnaire. The order of items within the PMT questionnaire was randomised to reduce order effects. At the conclusion of the study participants were invited to provided feedback on the survey via a free-text response box.

Data for this project was collected concurrently with data for a second project (described at [http://osf.io/87kwb](http://osf.io/87kwb)) in the following manner: 

- A single study listing both both studies was created on Amazon MTurk
- Interested participants read a Plain Language Statement that is relevant to both studies
- Consenting participants were sent to a single Qualtrics survey that contained the materials for both projects
- The randomisation feature within Qualtrics randomised participants to entry into either this project or the concurrent project
- Participants in this study were shown a message about climate change and answered questions relating to their climate change beliefs
- Participants in the concurrent project were shown a message about seasonal flu vaccination and answered questions to relating to their vaccination beliefs

Data collection for the two projects were administered in this manner in order to ensure that the samples are not contaminated (i.e. do not contain the same participants) as although the projects were not intended to be analysed or reported together, their structural similarity could cause unexpected effects for participants who participated in both (e.g. by resulting in unblinding). This method of data collection and the intention to analyse and report the studies seperately was documented in the pre-registration for both studies.

## Messages

Participants were randomised to receive one of six intervention messages or to a no message control group. Each intervention message was designed to target a single PMT construct.\footnote{A set of 24 candidate messages (4 per PMT construct) were first developed by EJK and ML and reviewed by BAM. These messages were then tested in a pilot study with a convienence sample of X Australian adults. Participants in the pilot study viewed a single candidate message relating to climate change and/or fossil fuel usage and responsed to a single item measure related to the construct the measure was intended to target (e.g. a severity message and a single item measure of severity). The mean response was calculated for each candidate message, the candidate message with the largest (or smallest in the case of MRR and RC) mean value on the construct measure was chosen for use within this study.}  

- "*The climate is changing. Climate change will lead to serious consequences in the United States including increased and more prolonged drought. Climate change is already contributing to water shortages around the globe.*" - Severity
- "*The climate is changing. These changes put everyone at risk. Whether or not you realize it, climate change is already affecting your life, by making extreme weather events more frequent and increasing food prices.*" - Susceptibility
- "*The climate is changing. Some people believe that climate change will lead to a more comfortable climate due to higher average daytime temperatures, but researchers agree that even in developed countries changes to our climate will disrupt basic necessities like food, clean air, and clean water.*" - Maladaptive Response Rewards
- "*We need to reduce our use of fossil fuels in order to reduce the risks of climate change. Many households can save hundreds of dollars each year simply by installing more efficient lights. Small changes like this make a difference and allow you to save money and help the environment at the same time.*" - Response Efficacy
- "*We need to reduce our use of fossil fuels in order to reduce the risks of climate change. Reducing your fossil fuel dependence is easy. You can change your use of fossil fuels with lots of little steps by driving less or doing one big load of laundry rather than multiple small loads.*" - Self-Efficacy
- "*We need to reduce our use of fossil fuels in order to reduce the risks of climate change. It doesn't take a lot of time and effort to reduce your fossil fuel usage, you can do something as simple as changing your electricity supply to one using more renewable energy sources.*" - Response Costs

## Measures

### Demographics

Participants completed a short demographic questionnaire at the beginning of the study. This included items regarding age, gender, highest level of education completed, annual household income, and political ideology. 

Political ideology was measured using three ideological self-placement items. Participants were asked to indicate "When it comes to ... would you consider yourself" with reference to "politics in general", "economic issues" and "social issues". Each item was meaured on a 0-10 point scale (0 = "Very Liberal": 10 = "Very Conservative").

### Intention

Intention was measured as the mean of three items (1= Strongly Disagree, 5 = Strongly Agree) regarding the referent behaviour "reduce my use of fossil fuels from now on". Higher scores indicate greater intention to reduce use of fossil fuels. 

### Severity

Participants indicated rated their agreement (from 1 = Strongly Disagree to 5 = Strongly Agree) with three items that indicated that the negative impact of climate change was severe. The three items were averaged to create a composite score. Higher scores indicate greater perceived severity of climate change. 

### Susceptibility

Participants indicated rated their agreement (from 1 = Strongly Disagree to 5 = Strongly Agree) with three items that indicated that they are vulnerable to the negative impacts of climate change. The three items were averaged to create a composite score. Higher scores indicate greater perceived susceptibility to negative impacts of climate change. 

### Maladaptive Response Rewards

Participants indicated rated their agreement (from 1 = Strongly Disagree to 5 = Strongly Agree) with three items that indicated that there are benefits of doing nothing regarding climate change or to climate change occuring. The three items were averaged to create a composite score. Higher scores indicate greater perceived maladaptive response rewards.

### Self-Efficacy

Participants indicated rated their agreement (from 1 = Strongly Disagree to 5 = Strongly Agree) with three items that indicated that they would be capable of reducing their use of fossil fuels. The three items were averaged to create a composite score. Higher scores indicate greater self-efficacy.

### Response Efficacy

Participants indicated rated their agreement (from 1 = Strongly Disagree to 5 = Strongly Agree) with three items that indicated that reducing their use of fossil fuels would be effective in reducing climate change. The three items were averaged to create a composite score. Higher scores indicate greater perceived response efficacy.

### Response Costs

Participants indicated rated their agreement (from 1 = Strongly Disagree to 5 = Strongly Agree) with three items that indicated that there are costs (including non-financial costs) associated with reducing fossil fuels. The three items were averaged to create a composite score. Higher scores indicate greater perceived response costs.

## Data analysis
We used `r cite_r("manuscripts/r-references.bib")` for all our analyses. All t-tests were conducted using Welsch's t-test. The alpha for the study was $\alpha$ = 0.0083.


# Results

## Pre-registered analyses
```{r severity_int}

t_out <- t.test(cc_int ~ as.factor(condition), 
                data = filter(climate, condition =="Control" | condition == "Severity"))

sev_tidy<-tidy(t_out)
sev<-apa_print(t_out)
```

```{r plotsev, warning=FALSE}
sevplot <- ggplot(filter(climate, condition =="Control" | condition == "Severity"), aes(condition, cc_sev)) + geom_boxplot(notch = TRUE) + theme_apa() + labs(x = "Message", y = "Severity Score")
```


```{r susceptibility_int}

t_out <- t.test(cc_int ~ as.factor(condition), 
                data=filter(climate, condition =="Control" | condition == "Susceptibility"))

sus_tidy<-tidy(t_out)
sus<-apa_print(t_out)
```

```{r plotsus, warning=FALSE}
susplot <- ggplot(filter(climate, condition =="Control" | condition == "Susceptibility"), aes(condition, cc_sus)) + geom_boxplot() + theme_apa() + labs(x = "Message", y = "Susceptibility Score")
```


```{r mrr_int, warning=FALSE}

t_out <- t.test(cc_int ~ as.factor(condition), 
                data = filter(climate, condition =="Control" | condition == "MRR"))

mrr_tidy<-tidy(t_out)
mrr<-apa_print(t_out)
```

```{r plotmrr, warning=FALSE}
mrrplot <- ggplot(filter(climate, condition =="Control" | condition == "MRR"), aes(condition, cc_mrr)) + geom_boxplot() + theme_apa()  + labs(x = "Message", y = "MRR Score")
```

```{r se_int}

t_out <- t.test(cc_int ~ as.factor(condition),
                data = filter(climate, condition =="Control" | condition == "Self-Efficacy"))

se_tidy<-tidy(t_out)
se<-apa_print(t_out)
```

```{r plotse, warning=FALSE}
seplot <- ggplot(filter(climate, condition =="Control" | condition == "Self-Efficacy"), aes(condition, cc_se)) + geom_boxplot() + theme_apa() + labs(x = "Message", y = "Self-Efficacy Score")
```

```{r re_int}

t_out <- t.test(cc_int ~ as.factor(condition), 
                data = filter(climate, condition =="Control" | condition == "Response Efficacy"))

re_tidy<-tidy(t_out)
re<-apa_print(t_out)
```

```{r plotre, warning=FALSE}
replot <- ggplot(filter(climate, condition =="Control" | condition == "Response Efficacy"), aes(condition, cc_re)) + geom_boxplot() + theme_apa()  + labs(x = "Message", y = "Response Efficacy Score")
```

```{r rc_int, warning=FALSE}

t_out <- t.test(cc_int ~ as.factor(condition), 
                filter(climate, condition =="Control" | condition == "Response Costs"))

rc_tidy<-tidy(t_out)
rc<-apa_print(t_out)
```

```{r plotrc, warning=FALSE}
rcplot <- ggplot(filter(climate, condition =="Control" | condition == "Response Costs"), aes(condition, cc_rc)) + geom_boxplot() + theme_apa() + labs(x = "Message", y = "Response Costs Score")
```

A series of t-tests (see Table \@ref(tab:int)) were conducted to investigate the impact of each message on intention to reduce fossil fuel consumption relative to control. Messages designed to increase self-efficacy (`r se$statistic`) and response efficacy (`r re$statistic`) were effective, although other messages were not (Severity: `r sev$statistic`; Susceptibility: `r sus$statistic`; MRR: `r mrr$statistic`; Response Costs: `r rc$statistic`).


```{r fig.height=10, fig.cap="Message vs. Control by Target Construct and Message", warning=FALSE}
ggplot(climate, aes(condition, cc_int)) + geom_boxplot() + theme_apa() + coord_flip() + labs(x = "", y = "Intention")
```

```{r fig.height=10, fig.cap="Message vs. Control by Target Construct and Message", warning=FALSE}
plot_grid(sevplot, susplot, mrrplot, seplot, replot, rcplot, ncol=2, labels = c("A", "B", "C", "D", "E", "F"))
```

```{r int, results="asis"}
int_tidy<-rbind(sev_tidy, sus_tidy, mrr_tidy, se_tidy, re_tidy, rc_tidy)

int_tidy$comparisons <- c("Control vs. Severity", 
                          "Control vs. Susceptibility", 
                          "Control vs. MRR", 
                          "Control vs. Self-efficacy", 
                          "Control vs. Response Efficacy", 
                          "Control vs. Response Costs")

int_tidy$p.value <- printp(int_tidy$p.value)

int_tidy <- int_tidy %>% 
  select(comparisons, estimate1, estimate2, statistic, p.value)

apa_table(int_tidy, caption = "Impact of interventions on intention to reduce fossil fuel consumption relative to control", placement = "htb", col.names=c("Comparisions", "Control Mean", "Intervention Mean", "\\textit{t}", "\\textit{p}"), align="lcccc")
```

```{r severity_coi}

test <-  filter(climate, condition =="Control" | condition == "Severity")
t_out <- t.test(test$cc_sev ~ as.factor(test$condition))

sev_tidy<-tidy(t_out)

sev<-apa_print(t_out)

```

```{r susceptibility_coi}

test <-  filter(climate, condition =="Control" | condition == "Susceptibility")
t_out <- t.test(test$cc_sus ~ as.factor(test$condition))

sus_tidy<-tidy(t_out)

sus<-apa_print(t_out)

```

```{r mrr_coi}

test <-  filter(climate, condition =="Control" | condition == "MRR")
t_out <- t.test(test$cc_mrr ~ as.factor(test$condition))

mrr_tidy<-tidy(t_out)

mrr<-apa_print(t_out)

```

```{r se_coi}

test <-  filter(climate, condition =="Control" | condition == "Self-Efficacy")
t_out <- t.test(test$cc_se ~ as.factor(test$condition))

se_tidy<-tidy(t_out)

se<-apa_print(t_out)

```

```{r re_coi}

test <-  filter(climate, condition =="Control" | condition == "Response Efficacy")
t_out <- t.test(test$cc_re ~ as.factor(test$condition))

re_tidy<-tidy(t_out)

re<-apa_print(t_out)

```

```{r rc_coi}

test <-  filter(climate, condition =="Control" | condition == "Response Costs")
t_out <- t.test(test$cc_rc ~ as.factor(test$condition))

rc_tidy<-tidy(t_out)

rc<-apa_print(t_out)

```

```{r coi, results="asis"}
coi_tidy<-rbind(sev_tidy, sus_tidy, mrr_tidy, se_tidy, re_tidy, rc_tidy)

coi_tidy$comparisons <- c("Control vs. Severity", 
                          "Control vs. Susceptibility", 
                          "Control vs. MRR", 
                          "Control vs. Self-efficacy", 
                          "Control vs. Response Efficacy", 
                          "Control vs. Response Costs")

coi_tidy$construct <- c("Severity", "Susceptibility", "MRR", "Self-efficacy", "Response Efficacy", "Response Costs")

coi_tidy$p.value <- printp(coi_tidy$p.value)

coi_tidy <- coi_tidy %>% 
  select(comparisons, construct, estimate1, estimate2, statistic, p.value)

apa_table(coi_tidy, caption = "Impact of interventions on target construct relative to control", placement = "htb", col.names=c("Comparisions", "Construct", "Control Mean", "Intervention Mean", "\\textit{t}", "\\textit{p}"), align="lcccc", small=TRUE)
```

T-tests were also conducted to investigate the impact of each message on the PMT construct it was designed to target (i.e. the effect of the *Self-Efficacy* message on *self-efficacy*) relative to Control. As shown in Table \@ref(tab:coi), only the Self-Efficacy message was successful in bringing about change in the the construct it was designed to target. 

## Exploratory analyses

In order to examine the potential pathway through which the Response Efficacy message leads to change in intention, an exploratory analysis was conducted to examine whether the Response Efficacy group differed from the Control group on any constructs other than response efficacy and intention. As shown in Table \@ref(tab:explor) the Response Efficacy group had significantly higher self-efficacy than the Control group and significantly lower perceieved response costs. 

```{r explor, results="asis"}

test <-  filter(climate, condition =="Control" | condition == "Response Efficacy")
t_out_sev <- t.test(test$cc_sev ~ as.factor(test$condition))
t_out_sus <- t.test(test$cc_sus ~ as.factor(test$condition))
t_out_mrr <- t.test(test$cc_mrr ~ as.factor(test$condition))
t_out_se <- t.test(test$cc_se ~ as.factor(test$condition))
t_out_rc <- t.test(test$cc_rc ~ as.factor(test$condition))

re_tidy<-rbind(tidy(t_out_sev), tidy(t_out_sus), tidy(t_out_mrr), tidy(t_out_se), tidy(t_out_rc))

re_tidy$construct <- c("Severity", "Susceptibility", "MRR", "Self-efficacy", "Response Costs")

re_tidy$p.value <- printp(re_tidy$p.value)

re_tidy <- re_tidy %>% 
  select(construct, estimate1, estimate2, statistic, p.value)

apa_table(re_tidy, caption="Exploratory analysis: impact of response efficacy message on other constructs", placement = "htb", col.names=c("Construct", "Control Mean", "Intervention Mean", "\\textit{t}", "\\textit{p}"), align="lcccc")

```


# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "manuscripts/r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
