---
title             : "Protection Motivation Theory Climate Change Denial"
shorttitle        : "PMT - CCD"

author: 
  - name          : "Emily J. Kothe"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Deakin University Locked Bag 20000"
    email         : "emily.kothe@deakin.edu.au"
  - name          : "Mathew Ling"
    affiliation   : "1"
  - name          : "Barbara A. Mullan"
    affiliation   : "2"  

affiliation:
  - id            : "1"
    institution   : "Deakin University, Geelong, Australia, Misinformation Lab, School of Psychology"
  - id            : "2"
    institution   : "Health Psychology and Behavioural Medicine Research Group, School of Psychology and Speech Pathology, Curtin University, Perth, Australia"
    
author_note: |
  Emily J. Kothe, Misinformation Lab, School of Psychology, Deakin University, Australia; Mathew Ling, Misinformation Lab, School of Psychology, Deakin University, Australia; Barbara A. Mullan, Health Psychology and Behavioural Medicine Research Group, School of Psychology and Speech Pathology, Curtin University, Perth, Australia.
  
  This research was supported in part by the Deakin University's Health ResAarch Capacity Building Grant ScHeme (HAtCH).  
  
abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "Protection Motivation Theory, Climate Change, Sustainability"
wordcount         : "X"

bibliography      : ["./r-references.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
library("papaja")
library(knitr)
library(readr)
library(dplyr)
```

```{r setglobal, cache = FALSE, include = TRUE}

opts_knit$set(root.dir = "..")

options(knitr.kable.NA = '')
```

```{r}
dat <- read_rds("./data/dat.rds")

climate <- dat %>% 
  filter(study=="Climate Change")
```
  Anthropogenic climate change represents an existential threat to humanity, affecting food security, water supply, the spread of infectious diseases, coastal inundation, and extreme weather events. Despite an overwhelming scientific consensus regarding the existence and harms of climate change, community belief in climate change is declining in a number of industrialised economies. The denial of the existence or severity of climate change is suggested to be influential in the support for climate mitigation policies and engagement in behaviours that might contribute to the reduction in harms assocaited with climate change.   

-- Fossil fuel use reduction
  The consumption of fossil fuels and the consequent increase in atmospheric carbon dioxide is considered the most influential factor in the changing climate. Historical increases in the abundance of greenhouse gasses in the atmosphere as obserrved in ice cores have been shown to be associated with the industrialisation of society. Therefore, strategies for mitigation of climate change focus on a combination of carbon sequestration and minimisation of fossil fuel use. 
  
  In 2015, fossil fuel sources produced 85.99% of global energy.  https://www.worldenergy.org/wp-content/uploads/2016/10/World-Energy-Resources-Full-report-2016.10.03.pdf 

-- Local Behaviours
  Household energy use constitutes one third of total energy use in Europe and the United States of America, (http://person.eu/downloads/PERSON-Stern-et-al-2016.pdf) 
  Reduction of energy use through behaviours such as using more efficient appliances, avoiding driving, and switching to low emission energy sources such as wind or solar, while unlikely to have any substantial effect in isolation, collectively may lead to substantial reductions with analyses suggesting the adoption of 17 behaviours resulting in up to a 7.4% reduction in total US emissions. (http://www.pnas.org/content/pnas/106/44/18452.full.pdf?spnCategory=155&spnDomain=2&spnContent=28&spnID=42103)


  https://s3.amazonaws.com/academia.edu.documents/33137138/1-s2.0-S0301421512008506-main.pdf?AWSAccessKeyId=AKIAIWOWYYGZ2Y53UL3A&Expires=1533531297&Signature=nynJvhbTZxLAJUBSNAg61OEco%2BU%3D&response-content-disposition=inline%3B%20filename%3DAnalysis_of_the_performance_of_domestic.pdf

--  Protection Motivation theory


# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

Participants were recruited via Amazon MTurk. See Table \@ref(tab:demo) for a summary of participant characteristics. After data cleaning, `r nrow(climate)` participants were included in this study.

```{r demo, results='asis', warning=FALSE}
## climate_demo.csv is generated by create_tables.R

tab <- read_csv("manuscripts/climate_demo.csv")

names(tab)[1] <- "Demographic Characteristic"

Variables<-as.list(c(4:10, 12:19, 21:33))

papaja::apa_table(tab, caption="Demographic characteristics by study", stub_indents= Variables, longtable = TRUE)
```

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


Behaviours such as dietary change (https://www-sciencedirect-com.ezproxy-f.deakin.edu.au/science/article/pii/S0959652614012931#fig1)

\newpage

# References
```{r create_r-references}
r_refs(file = "manuscripts/r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
