---
title             : "Protection Motivation Theory Climate Change Denial"
shorttitle        : "PMT - CCD"

author: 
  - name          : "Emily J. Kothe"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Deakin University Locked Bag 20000"
    email         : "emily.kothe@deakin.edu.au"
  - name          : "Mathew Ling"
    affiliation   : "1"
  - name          : "Barbara A. Mullan"
    affiliation   : "2"  

affiliation:
  - id            : "1"
    institution   : "Deakin University, Geelong, Australia, Misinformation Lab, School of Psychology"
  - id            : "2"
    institution   : "Health Psychology and Behavioural Medicine Research Group, School of Psychology and Speech Pathology, Curtin University, Perth, Australia"
    
author_note: |
  Emily J. Kothe, Misinformation Lab, School of Psychology, Deakin University, Australia; Mathew Ling, Misinformation Lab, School of Psychology, Deakin University, Australia; Barbara A. Mullan, Health Psychology and Behavioural Medicine Research Group, School of Psychology and Speech Pathology, Curtin University, Perth, Australia.
  
  This research was supported in part by the Deakin University's Health ResAarch Capacity Building Grant ScHeme (HAtCH).  
  
abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "Protection Motivation Theory, Climate Change, Sustainability"
wordcount         : "X"

bibliography      : ["../manuscripts/r-references.bib", "../manuscripts/refs.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
library("papaja")
library(knitr)
library(readr)
library(tidyr)
library(dplyr)
library(broom)
library(here)
library(ggplot2)
library(cowplot)
library(psych)
library(labelled)
library(tableone)
```

```{r setglobal, cache = FALSE, include = TRUE}

opts_knit$set(root.dir = "..")

options(knitr.kable.NA = '')
```

```{r}
dat <- read_rds(here("data", "dat.rds"))

climate <- dat %>% 
  filter(study=="Climate Change")
```

Anthropogenic climate change represents an existential threat to humanity, affecting food security, water supply, the spread of infectious diseases, coastal inundation, and extreme weather events <!--- need some references for this point -->. The consumption of fossil fuels and the consequent increase in atmospheric carbon dioxide is considered the most influential factor in the changing climate <!--- need some references for this point -->. Therefore, strategies for mitigation of climate change focus on a combination of carbon sequestration and minimisation of fossil fuel use <!--- need some references for this point -->. Household energy use constitutes one third of total energy use in Europe and the United States of America [@stern2016opportunities]. In turn, the majority of global energy, included that used for household energy, is generated from fossil fuels [@council2016world]. Large scale adoption of behaviours that reduce fossil fuel consumption such as using more efficient appliances, avoiding driving, and switching to low emission energy sources such as wind or solar has the potential to lead to substantial reductions in total emissions [@dietz2009household; @wynes2017climate]. While individual-level behaviour will not be sufficent to meet global emissions targets alone, it plays an important role in the global response to climate change because the speed of uptake of individual behaviour can outpace the speed at which systematic changes such as construction of "green energy" based electricity grids and implementation of carbon pricing and trade policies can occur [@dietz2009household; @wynes2017climate].

[Something about that textbook study showing these behaviours have been widely advocated]. However, individuals' engagement in behaviours to reduce usage of fossil fuels remains low <!--- need some references for this point -->. 
 
  
  In 2015, fossil fuel sources produced 85.99% of global energy.  [@council2016world]

-- Local Behaviours

@aman2013analysis


## Protection Motivation theory

PMT was specifically developed to understand adaptive and maladaptive responses to persuasive messages17. Adaptive responses are characterised as increased performance of protective behaviours in response to persuasive messages. In contrast, maladaptive responses are those which drive continued failure to engage in protective behaviours. According to PMT, the propensity to engage adaptively with persuasive messages is determined by beliefs that people have about engaging in (or not engaging in) the desired protective behaviour and about the threatened event (i.e. contracting an infectious disease/climate change). Individual’s beliefs are categorised into six constructs:
- Severity: perceived seriousness of the negative consequences of the threatened event
- Susceptibility: perceived vulnerability to the negative consequences of the threatened event
- Maladaptive response rewards: Benefits of the performance of the maladaptive behaviour
- Response efficacy: The perceived effectiveness of the recommended preventative behaviour in averting the occurrence or negative consequences of the threatened event
- Self-efficacy: confidence in one’s ability to successfully perform the preventative behaviour
- Response costs: The barriers to performance of the preventative behaviour
According to PMT, motivation to engage in the protective behaviour is determined by two parallel processes: Threat Appraisal and Coping Appraisal. Threat Appraisal is determined by beliefs about the severity, susceptibility, and rewards of maladaptive behaviour. Coping Appraisal is determined by response costs, response efficacy, and self-efficacy. Individuals are motivated to engage in protective behaviour when they believe that lack of action poses a threat to themselves (high threat appraisal) and that performing the preventative behaviour can ameliorate that threat (high coping appraisal). In contrast, maladaptive responses may occur when threat appraisal is low (i.e. when the maladaptive behaviour does not pose a sufficiently serious threat) or when threat appraisal is high and coping appraisal is low (i.e. the adverse event is threatening but the recommended behaviour is not thought to be an effective way to reduce the risk). 

Previous studies  have found that coping and threat appraisal predict adaptive behaviours in response to climate change19, 20, 21

Meta-analysis indicates that persuasive messages that seek to manipulate PMT constructs are effective in changing corresponding beliefs25. By investigating messages that vary in the extent to which they elicit change in different PMT constructs researchers have used PMT identify the persuasive messages that are most likely to be effective at provoking adaptive responses. For example, one study found that anti-smoking mass media campaigns were most effective at motivating adolescents (n=1667) to avoid smoking when they emphasised specific severity perceptions (namely risk of social disapproval)26. Importantly, messages that sought to increase perceived severity of health risks were undermined by low perceived susceptibility26. 

However, to date there are no experimental studies investigating whether the targeting of PMT constructs will increase adaptive behaviours climate change denial, and no studies that had systematically investigated the relative impact of messages targeting different PMT constructs within these domains. 

## Hypotheses 
1. The primary outcome is protection motivation (defined as the intention to be vaccinated against seasonable influenza). It is hypothesised that intervention messages targeting PMT constructs will increase intention to be vaccinated relative to control.  
2. The secondary outcomes are the PMT constructs. It is hypothesised that intervention messages targeting a given PMT construct will increase/decrease that construct relative to control. Specifically,  
    a. Relative to control, the message targeting response cost will decrease perceived response cost 
    b. Relative to control, the message targeting maladaptive response rewards will decrease perceived maladaptive response rewards  
    c. Relative to control, the message targeting response efficacy will increase perceived response efficacy 
    d. Relative to control, the message targeting severity will increase perceived severity 
    e. Relative to control, the message targeting susceptibility will increase perceived susceptibility 
    f. Relative to control, the message targeting self efficacy will increase  self-efficacy 

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) --> This study was pre-registered using the template for pre-registration in social psychology developed by @van2016pre. The pre-registration for this project is available at: [https://osf.io/2g6bq/](https://osf.io/2g6bq/).

## Participants

Participants were recruited via Amazon MTurk to take part in a study on "Short study of responses to messages about scientific issues" in exchange for $1.10USD in Amazon credit.  Sample size was determined *a priori*, we aimed to recruit a minimum of 526 participants per cell in order to detect an effect of d =.2, with 80% power, and an alpha of 0.0083. To account for missingness, we oversampled each cell by 20, leading to recruitment target of 546 per condition and a total recruitment target of 3822. After removal of duplicate and incomplete submissions\footnote{Complete removal of data from participants with duplicate submissions was required in order to avoid contamination between conditions. Removal of incomplete submissions was required because submission of the completed survey indicated consent}, `r printnum(nrow(climate))` participants were included in this study. The final number of participants in each condition is shown in Table \@ref(tab:cond).

```{r cond, results="asis"}

cond <- as.data.frame(table(climate$condition))

apa_table(cond, caption = "Final N per Condition", placement = "htb", col.names=c("Condition", "N"))

```

Three participants reported an age value that was not plausible (i.e. below the allowed age for registration on MTurk or above 200 years). These ages were converted to missing but the responses of those participants were otherwise retained. Gender was recorded using a free-text field and then categorised manually, Four participants provided a response to this item that could not be meaningfully catergorised (in all cases these representated responses that did not appear to reflect gender identity e.g. "%" or "40"). These responses were converted to missing but the responses of those participants were otherwise retained. See Table \@ref(tab:demo) for a summary of participant characteristics. 

```{r demo, results='asis', warning=FALSE}

climate <- climate %>% 
  set_variable_labels(
    age = "Age in years",
    education = "Highest level of education",
    gender = "Gender",
    household_income = "Annual household income", 
    ideology_general = "Ideology - General", 
    ideology_economic = "Ideology - Economic",
    ideology_social = "Ideology - Social")

tab <- CreateTableOne(vars = c("age", 
                             "education",
                             "gender",
                             "household_income", 
                             "ideology_general", 
                             "ideology_economic", 
                             "ideology_social"), 
                    data = climate, test = FALSE)

tab <- print(tab, varLabels = T, printToggle = FALSE)

papaja::apa_table(tab, caption="Demographic characteristics of participants", longtable = TRUE)
```

## Procedure

The study was administered via the online survey platform Qualtrics. Participants who chose to take part in the study completed an online questionnaire that included all measures and the experimental manipulation.

The first component of the questionnaire included measures of demographic variables (e.g. age, gender, household income). Participants were then randomly allocated (by Qualtrics) to one of the six intervention groups or control. Individuals allocated to receive an intervention message were  shown a message related instruction and then the target message.  Individuals in the control group did not receive the instruction or any message and instead proceeded directly to next part of the survey. Participants were not notified of their condition (or their allocation to a no message condition). In the third part of the questionnaire, participants completed the PMT questionnaire. The order of items within the PMT questionnaire was randomised to reduce order effects. At the conclusion of the study participants were invited to provided feedback on the survey via a free-text response box.

Data for this project was collected concurrently with data for a second project (described at [http://osf.io/87kwb](http://osf.io/87kwb)) in the following manner: 

- A single study listing both both studies was created on Amazon MTurk
- Interested participants read a Plain Language Statement that is relevant to both studies
- Consenting participants were sent to a single Qualtrics survey that contained the materials for both projects
- The randomisation feature within Qualtrics randomised participants to entry into either this project or the concurrent project
- Participants in this study were shown a message about climate change and answered questions relating to their climate change beliefs
- Participants in the concurrent project were shown a message about seasonal flu vaccination and answered questions to relating to their vaccination beliefs

Data collection for the two projects were administered in this manner in order to ensure that the samples are not contaminated (i.e. do not contain the same participants) as although the projects were not intended to be analysed or reported together, their structural similarity could cause unexpected effects for participants who participated in both (e.g. by resulting in unblinding). This method of data collection and the intention to analyse and report the studies seperately was documented in the pre-registration for both studies.

## Messages

Participants were randomised to receive one of six intervention messages or to a no message control group. Each intervention message was designed to target a single PMT construct.\footnote{A set of 24 candidate messages (4 per PMT construct) were first developed by EJK and ML and reviewed by BAM. These messages were then tested in a pilot study with a convienence sample of X Australian adults. Participants in the pilot study viewed a single candidate message relating to climate change and/or fossil fuel usage and responsed to a single item measure related to the construct the measure was intended to target (e.g. a severity message and a single item measure of severity). The mean response was calculated for each candidate message, the candidate message with the largest (or smallest in the case of MRR and RC) mean value on the construct measure was chosen for use within this study.}  

- "*The climate is changing. Climate change will lead to serious consequences in the United States including increased and more prolonged drought. Climate change is already contributing to water shortages around the globe.*" - Severity
- "*The climate is changing. These changes put everyone at risk. Whether or not you realize it, climate change is already affecting your life, by making extreme weather events more frequent and increasing food prices.*" - Susceptibility
- "*The climate is changing. Some people believe that climate change will lead to a more comfortable climate due to higher average daytime temperatures, but researchers agree that even in developed countries changes to our climate will disrupt basic necessities like food, clean air, and clean water.*" - Maladaptive Response Rewards
- "*We need to reduce our use of fossil fuels in order to reduce the risks of climate change. Many households can save hundreds of dollars each year simply by installing more efficient lights. Small changes like this make a difference and allow you to save money and help the environment at the same time.*" - Response Efficacy
- "*We need to reduce our use of fossil fuels in order to reduce the risks of climate change. Reducing your fossil fuel dependence is easy. You can change your use of fossil fuels with lots of little steps by driving less or doing one big load of laundry rather than multiple small loads.*" - Self-Efficacy
- "*We need to reduce our use of fossil fuels in order to reduce the risks of climate change. It doesn't take a lot of time and effort to reduce your fossil fuel usage, you can do something as simple as changing your electricity supply to one using more renewable energy sources.*" - Response Costs

## Measures

### Demographics

Participants completed a short demographic questionnaire at the beginning of the study. This included items regarding age, gender, highest level of education completed, annual household income, and political ideology. 

Political ideology was measured using three ideological self-placement items. Participants were asked to indicate "When it comes to ... would you consider yourself" with reference to "politics in general", "economic issues" and "social issues". Each item was meaured on a 0-10 point scale (0 = "Very Liberal": 10 = "Very Conservative").

### Intention

Intention was measured as the mean of three items (1= Strongly Disagree, 5 = Strongly Agree) regarding the referent behaviour "reduce my use of fossil fuels from now on". Higher scores indicate greater intention to reduce use of fossil fuels. 

### Severity

Participants indicated rated their agreement (from 1 = Strongly Disagree to 5 = Strongly Agree) with three items that indicated that the negative impact of climate change was severe. The three items were averaged to create a composite score. Higher scores indicate greater perceived severity of climate change. 

### Susceptibility

Participants indicated rated their agreement (from 1 = Strongly Disagree to 5 = Strongly Agree) with three items that indicated that they are vulnerable to the negative impacts of climate change. The three items were averaged to create a composite score. Higher scores indicate greater perceived susceptibility to negative impacts of climate change. 

### Maladaptive Response Rewards

Participants indicated rated their agreement (from 1 = Strongly Disagree to 5 = Strongly Agree) with three items that indicated that there are benefits of doing nothing regarding climate change or to climate change occuring. The three items were averaged to create a composite score. Higher scores indicate greater perceived maladaptive response rewards.

### Self-Efficacy

Participants indicated rated their agreement (from 1 = Strongly Disagree to 5 = Strongly Agree) with three items that indicated that they would be capable of reducing their use of fossil fuels. The three items were averaged to create a composite score. Higher scores indicate greater self-efficacy.

### Response Efficacy

Participants indicated rated their agreement (from 1 = Strongly Disagree to 5 = Strongly Agree) with three items that indicated that reducing their use of fossil fuels would be effective in reducing climate change. The three items were averaged to create a composite score. Higher scores indicate greater perceived response efficacy.

### Response Costs

Participants indicated rated their agreement (from 1 = Strongly Disagree to 5 = Strongly Agree) with three items that indicated that there are costs (including non-financial costs) associated with reducing fossil fuels. The three items were averaged to create a composite score. Higher scores indicate greater perceived response costs.

## Data analysis
We used `r cite_r("manuscripts/r-references.bib")` for all our analyses. All t-tests were conducted using Welsch's t-test. The alpha for the study was $\alpha$ = 0.0083.


# Results

## Pre-registered analyses
```{r severity_int}

t_out <- t.test(cc_int ~ as.factor(condition), 
                data = filter(climate, condition =="Control" | condition == "Severity"))

sev_tidy<-tidy(t_out)
sev<-apa_print(t_out)
```

```{r plotsev, warning=FALSE}
sevplot <- ggplot(filter(climate, condition =="Control" | condition == "Severity"), aes(condition, cc_sev)) + geom_boxplot(notch = TRUE) + theme_apa() + labs(x = "Message", y = "Severity Score")
```


```{r susceptibility_int}

t_out <- t.test(cc_int ~ as.factor(condition), 
                data=filter(climate, condition =="Control" | condition == "Susceptibility"))

sus_tidy<-tidy(t_out)
sus<-apa_print(t_out)
```

```{r plotsus, warning=FALSE}
susplot <- ggplot(filter(climate, condition =="Control" | condition == "Susceptibility"), aes(condition, cc_sus)) + geom_boxplot(notch = TRUE) + theme_apa() + labs(x = "Message", y = "Susceptibility Score")
```


```{r mrr_int, warning=FALSE}

t_out <- t.test(cc_int ~ as.factor(condition), 
                data = filter(climate, condition =="Control" | condition == "MRR"))

mrr_tidy<-tidy(t_out)
mrr<-apa_print(t_out)
```

```{r plotmrr, warning=FALSE}
mrrplot <- ggplot(filter(climate, condition =="Control" | condition == "MRR"), aes(condition, cc_mrr)) + geom_boxplot(notch = TRUE) + theme_apa()  + labs(x = "Message", y = "MRR Score")
```

```{r se_int}

t_out <- t.test(cc_int ~ as.factor(condition),
                data = filter(climate, condition =="Control" | condition == "Self-Efficacy"))

se_tidy<-tidy(t_out)
se<-apa_print(t_out)
```

```{r plotse, warning=FALSE}
seplot <- ggplot(filter(climate, condition =="Control" | condition == "Self-Efficacy"), aes(condition, cc_se)) + geom_boxplot(notch = TRUE) + theme_apa() + labs(x = "Message", y = "Self-Efficacy Score")
```

```{r re_int}

t_out <- t.test(cc_int ~ as.factor(condition), 
                data = filter(climate, condition =="Control" | condition == "Response Efficacy"))

re_tidy<-tidy(t_out)
re<-apa_print(t_out)
```

```{r plotre, warning=FALSE}
replot <- ggplot(filter(climate, condition =="Control" | condition == "Response Efficacy"), aes(condition, cc_re)) + geom_boxplot(notch = TRUE) + theme_apa()  + labs(x = "Message", y = "Response Efficacy Score")
```

```{r rc_int, warning=FALSE}

t_out <- t.test(cc_int ~ as.factor(condition), 
                filter(climate, condition =="Control" | condition == "Response Costs"))

rc_tidy<-tidy(t_out)
rc<-apa_print(t_out)
```

```{r plotrc, warning=FALSE}
rcplot <- ggplot(filter(climate, condition =="Control" | condition == "Response Costs"), aes(condition, cc_rc)) + geom_boxplot(notch = TRUE) + theme_apa() + labs(x = "Message", y = "Response Costs Score")
```

A series of t-tests (see Table \@ref(tab:int)) were conducted to investigate the impact of each message on intention to reduce fossil fuel consumption relative to control. Messages designed to increase self-efficacy (`r se$statistic`) and response efficacy (`r re$statistic`) were effective, although other messages were not (Severity: `r sev$statistic`; Susceptibility: `r sus$statistic`; MRR: `r mrr$statistic`; Response Costs: `r rc$statistic`).


```{r fig.height=10, fig.cap="Message vs. Control by Target Construct and Message", warning=FALSE}
ggplot(climate, aes(condition, cc_int)) + geom_boxplot(notch = TRUE) + theme_apa() + coord_flip() + labs(x = "", y = "Intention")
```

```{r fig.height=10, fig.cap="Message vs. Control by Target Construct and Message", warning=FALSE}
plot_grid(sevplot, susplot, mrrplot, seplot, replot, rcplot, ncol=2, labels = c("A", "B", "C", "D", "E", "F"))
```

```{r int, results="asis"}
clim_sum <- climate  %>% 
  group_by(factor(condition)) %>% 
  summarise(int_sd = sd(cc_int, na.rm=TRUE), int_n = sum(!is.na(cc_int)), 
            re_sd  = sd(cc_re, na.rm=TRUE),  re_n  = sum(!is.na(cc_re)),
            rc_sd  = sd(cc_rc, na.rm=TRUE),  rc_n  = sum(!is.na(cc_rc)),
            mrr_sd = sd(cc_mrr, na.rm=TRUE), mrr_n = sum(!is.na(cc_mrr)),
            se_sd  = sd(cc_se, na.rm=TRUE),  se_n  = sum(!is.na(cc_se)),
            sev_sd = sd(cc_sev, na.rm=TRUE), sev_n = sum(!is.na(cc_sev)),
            sus_sd = sd(cc_sus, na.rm=TRUE), sus_n = sum(!is.na(cc_sus))
            )
names(clim_sum)[1] <- "condition"

tab3 <- clim_sum %>%
  select(condition, int_sd, int_n) %>% 
  mutate(ctr_sd = clim_sum$int_sd[clim_sum$condition=="Control"],
         ctr_n = clim_sum$int_n[clim_sum$condition=="Control"], 
         comparisons = case_when(
           condition == "MRR" ~ "Control vs. MRR",
           condition == "Severity" ~ "Control vs. Severity",
           condition == "Susceptibility" ~ "Control vs. Susceptibility",
           condition == "Self-Efficacy" ~ "Control vs. Self-efficacy",
           condition == "Response Efficacy" ~ "Control vs. Response Efficacy",
           condition == "Response Costs" ~ "Control vs. Response Costs"),
          ctr_n = as.character(ctr_n), 
          int_n = as.character(int_n)
         ) %>% 
  filter(condition != "Control")

int_tidy<-rbind(sev_tidy, sus_tidy, mrr_tidy, se_tidy, re_tidy, rc_tidy)

int_tidy$comparisons <- c("Control vs. Severity", 
                          "Control vs. Susceptibility", 
                          "Control vs. MRR", 
                          "Control vs. Self-efficacy", 
                          "Control vs. Response Efficacy", 
                          "Control vs. Response Costs")

int_tidy$p.value <- printp(int_tidy$p.value)

int_tidy <- int_tidy  %>% 
  left_join(tab3, by = "comparisons") %>% 
  select(comparisons, estimate1, ctr_sd, ctr_n, estimate2, int_sd, int_n, statistic, p.value)

apa_table(int_tidy, caption = "Impact of interventions on intention to reduce fossil fuel consumption relative to control", placement = "htb", col.names=c("Comparisions", "Control Mean", "Control SD", "Control n", "Int. Mean", "Int. SD", "Int. n", "\\textit{t}", "\\textit{p}"), align="lcccccccc", landscape = TRUE, note = "MRR = Maladaptive Response Rewards")
```

```{r severity_coi}

test <-  filter(climate, condition =="Control" | condition == "Severity")
t_out <- t.test(test$cc_sev ~ as.factor(test$condition))

sev_tidy<-tidy(t_out)

sev<-apa_print(t_out)

```

```{r susceptibility_coi}

test <-  filter(climate, condition =="Control" | condition == "Susceptibility")
t_out <- t.test(test$cc_sus ~ as.factor(test$condition))

sus_tidy<-tidy(t_out)

sus<-apa_print(t_out)

```

```{r mrr_coi}

test <-  filter(climate, condition =="Control" | condition == "MRR")
t_out <- t.test(test$cc_mrr ~ as.factor(test$condition))

mrr_tidy<-tidy(t_out)

mrr<-apa_print(t_out)

```

```{r se_coi}

test <-  filter(climate, condition =="Control" | condition == "Self-Efficacy")
t_out <- t.test(test$cc_se ~ as.factor(test$condition))

se_tidy<-tidy(t_out)

se<-apa_print(t_out)

```

```{r re_coi}

test <-  filter(climate, condition =="Control" | condition == "Response Efficacy")
t_out <- t.test(test$cc_re ~ as.factor(test$condition))

re_tidy<-tidy(t_out)

re<-apa_print(t_out)

```

```{r rc_coi}

test <-  filter(climate, condition =="Control" | condition == "Response Costs")
t_out <- t.test(test$cc_rc ~ as.factor(test$condition))

rc_tidy<-tidy(t_out)

rc<-apa_print(t_out)

```

```{r coi, results="asis"}

tab4 <- clim_sum %>%
  select(-one_of("int_sd", "int_n")) %>% 
  gather(-condition, key = "stat", value = "value") %>%
  separate(stat, into= c("construct", "stat"), sep="_") %>% 
  spread(key = stat, value= value)

tab4_ctr <-tab4 %>% 
  filter(condition=="Control") %>% 
  select(construct, ctr_n = n, ctr_sd = sd)

tab4 <- tab4 %>% 
  filter(condition != "Control") %>% 
  select(condition, construct, int_n = n, int_sd = sd) %>% 
  inner_join(tab4_ctr, by = "construct") %>% 
  mutate(construct = case_when(
          construct == "mrr" ~ "MRR",
          construct == "sev" ~ "Severity",
          construct == "sus" ~ "Susceptibility",
          construct == "se" ~ "Self-efficacy",
          construct == "re" ~ "Response Efficacy",
          construct == "rc" ~ "Response Costs"),
         comparisons = case_when(
           condition == "MRR" ~ "Control vs. MRR",
           condition == "Severity" ~ "Control vs. Severity",
           condition == "Susceptibility" ~ "Control vs. Susceptibility",
           condition == "Self-Efficacy" ~ "Control vs. Self-efficacy",
           condition == "Response Efficacy" ~ "Control vs. Response Efficacy",
           condition == "Response Costs" ~ "Control vs. Response Costs"),
          ctr_n = as.character(ctr_n), 
          int_n = as.character(int_n)
  ) 

coi_tidy<-rbind(sev_tidy, sus_tidy, mrr_tidy, se_tidy, re_tidy, rc_tidy)

coi_tidy$comparisons <- c("Control vs. Severity", 
                          "Control vs. Susceptibility", 
                          "Control vs. MRR", 
                          "Control vs. Self-efficacy", 
                          "Control vs. Response Efficacy", 
                          "Control vs. Response Costs")

coi_tidy$construct <- c("Severity", "Susceptibility", "MRR", "Self-efficacy", "Response Efficacy", "Response Costs")

coi_tidy$p.value <- printp(coi_tidy$p.value)

coi_tidy <- coi_tidy %>% 
  left_join(tab4, by = c("comparisons", "construct")) %>% 
  select(comparisons, construct, estimate1, ctr_sd, ctr_n, estimate2, int_sd, int_n, statistic, p.value)

apa_table(coi_tidy, caption = "Impact of interventions on target construct relative to control", placement = "htb", col.names = c("Comparisions", "Construct", "Control Mean", "Control SD", "Control n", "Int. Mean", "Int. SD", "Int. n",  "\\textit{t}", "\\textit{p}"), align = "llcccccccc", small = TRUE, landscape = TRUE, note = "MRR = Maladaptive Response Rewards")
```

T-tests were also conducted to investigate the impact of each message on the PMT construct it was designed to target (i.e. the effect of the *Self-Efficacy* message on *self-efficacy*) relative to Control. As shown in Table \@ref(tab:coi), only the Self-Efficacy message was successful in bringing about change in the the construct it was designed to target. 

## Exploratory analyses

In order to examine the potential pathway through which the Response Efficacy message leads to change in intention, an exploratory analysis was conducted to examine whether the Response Efficacy group differed from the Control group on any constructs other than response efficacy and intention. As shown in Table \@ref(tab:explor) the Response Efficacy group had significantly higher self-efficacy than the Control group and significantly lower perceieved response costs. 

```{r explor, results="asis"}
re_summ <- clim_sum %>% 
  select(-one_of("int_sd", "int_n")) %>% 
  gather(-condition, key = "stat", value = "value") %>%
  separate(stat, into= c("construct", "stat"), sep="_") %>% 
  spread(key = stat, value= value) 

re_ctr <-re_summ %>% 
  filter(condition=="Control") %>% 
  select(construct, ctr_n = n, ctr_sd = sd)

re_summ <- re_summ %>% 
  filter(condition == "Response Efficacy") %>% 
  select(condition, construct, int_n =n, int_sd = sd) %>% 
  inner_join(re_ctr, by = "construct") %>% 
  mutate(construct = case_when(
          construct == "mrr" ~ "MRR",
          construct == "sev" ~ "Severity",
          construct == "sus" ~ "Susceptibility",
          construct == "se" ~ "Self-efficacy",
          construct == "re" ~ "Response Efficacy",
          construct == "rc" ~ "Response Costs"), 
         int_n = as.character(int_n), 
         ctr_n = as.character(ctr_n))

test <-  filter(climate, condition =="Control" | condition == "Response Efficacy")
t_out_sev <- t.test(test$cc_sev ~ as.factor(test$condition))
t_out_sus <- t.test(test$cc_sus ~ as.factor(test$condition))
t_out_mrr <- t.test(test$cc_mrr ~ as.factor(test$condition))
t_out_se <- t.test(test$cc_se ~ as.factor(test$condition))
t_out_rc <- t.test(test$cc_rc ~ as.factor(test$condition))

re_tidy<-rbind(tidy(t_out_sev), tidy(t_out_sus), tidy(t_out_mrr), tidy(t_out_se), tidy(t_out_rc))

re_tidy$construct <- c("Severity", "Susceptibility", "MRR", "Self-efficacy", "Response Costs")

re_tidy$p.value <- printp(re_tidy$p.value)

re_tidy <- re_tidy %>% 
  left_join(re_summ, by = "construct") %>% 
  select(construct, estimate1, ctr_sd, ctr_n, estimate2, int_sd, int_n, statistic, p.value)

apa_table(re_tidy, 
          caption = "Exploratory analysis: impact of response efficacy message on other constructs", 
          col.names = c("Construct", "Control Mean", "Control SD", "Control n", "Int. Mean", "Int. SD", "Int. n", "\\textit{t}", "\\textit{p}"),
          placement = "htb", align="lcccccccc", small = TRUE, note = "MRR = Maladaptive Response Rewards")

```

We conducted a mediation analysis to investigate the extent to which self-efficacy mediates the relationship between condition (Control vs. Self-Efficacy Message) and intention.

```{r}
data <- filter(climate, condition =="Control" | condition == "Self-Efficacy")

data <- data %>%
  mutate(cond_new = case_when(
    condition == "Control" ~ 0, 
    condition == "Self-Efficacy" ~ 1
  ) )

mediation_se <- mediate(cc_int ~ cond_new + (cc_se), data = data, n.iter = 5000)

psych::mediate.diagram(medi = mediation_se, main = "Self-Efficacy as a mediator of the Condition - Intention relationship")

```



# Discussion


Behaviours such as dietary change [@hallstrom2015environmental]

\newpage

# References
```{r create_r-references}
r_refs(file = "manuscripts/r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
