---
title             : "Protection Motivation Theory Climate Change Denial"
shorttitle        : "PMT - CCD"

author: 
  - name          : "Emily J. Kothe"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Deakin University Locked Bag 20000"
    email         : "emily.kothe@deakin.edu.au"
  - name          : "Mathew Ling"
    affiliation   : "1"
  - name          : "Barbara A. Mullan"
    affiliation   : "2"  

affiliation:
  - id            : "1"
    institution   : "Deakin University, Geelong, Australia, Misinformation Lab, School of Psychology"
  - id            : "2"
    institution   : "Health Psychology and Behavioural Medicine Research Group, School of Psychology and Speech Pathology, Curtin University, Perth, Australia"
    
author_note: |
  Emily J. Kothe, Misinformation Lab, School of Psychology, Deakin University, Australia; Mathew Ling, Misinformation Lab, School of Psychology, Deakin University, Australia; Barbara A. Mullan, Health Psychology and Behavioural Medicine Research Group, School of Psychology and Speech Pathology, Curtin University, Perth, Australia.
  
  This research was supported in part by the Deakin University's Health ResAarch Capacity Building Grant ScHeme (HAtCH).  
  
abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "Protection Motivation Theory, Climate Change, Sustainability"
wordcount         : "X"

bibliography      : ["./r-references.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
library("papaja")
library(knitr)
library(readr)
library(dplyr)
```

```{r setglobal, cache = FALSE, include = TRUE}

opts_knit$set(root.dir = "..")

options(knitr.kable.NA = '')
```

```{r}
dat <- read_rds("./data/dat.rds")

climate <- dat %>% 
  filter(study=="Climate Change")
```


# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

Participants were recruited via Amazon MTurk. See Table \@ref(tab:demo) for a summary of participant characteristics. After data cleaning, `r nrow(climate)` participants were included in this study.

```{r demo, results='asis', warning=FALSE}
## climate_demo.csv is generated by create_tables.R

tab <- read_csv("manuscripts/climate_demo.csv")

names(tab)[1] <- "Demographic Characteristic"

Variables<-as.list(c(4:10, 12:19, 21:33))

papaja::apa_table(tab, caption="Demographic characteristics by study", stub_indents= Variables, longtable = TRUE)
```

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "manuscripts/r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
