---
title             : "Protection Motivation Theory Climate Change Denial"
shorttitle        : "PMT - CCD"

author: 
  - name          : "Emily J. Kothe"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Deakin University Locked Bag 20000"
    email         : "emily.kothe@deakin.edu.au"
  - name          : "Mathew Ling"
    affiliation   : "1"
  - name          : "Barbara A. Mullan"
    affiliation   : "2"  

affiliation:
  - id            : "1"
    institution   : "Deakin University, Geelong, Australia, Misinformation Lab, School of Psychology"
  - id            : "2"
    institution   : "Health Psychology and Behavioural Medicine Research Group, School of Psychology and Speech Pathology, Curtin University, Perth, Australia"
    
author_note: |
  Emily J. Kothe, Misinformation Lab, School of Psychology, Deakin University, Australia; Mathew Ling, Misinformation Lab, School of Psychology, Deakin University, Australia; Barbara A. Mullan, Health Psychology and Behavioural Medicine Research Group, School of Psychology and Speech Pathology, Curtin University, Perth, Australia.
  
  This research was supported in part by the Deakin University's Health ResAarch Capacity Building Grant ScHeme (HAtCH).  
  
abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "Protection Motivation Theory, Climate Change, Sustainability"
wordcount         : "X"

bibliography      : ["../manuscripts/r-references.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
library("papaja")
library(knitr)
library(readr)
library(dplyr)
library(broom)
library(here)
```

```{r setglobal, cache = FALSE, include = TRUE}

opts_knit$set(root.dir = "..")

options(knitr.kable.NA = '')
```

```{r}
dat <- read_rds(here("data", "dat.rds"))

climate <- dat %>% 
  filter(study=="Climate Change")
```


# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

Participants were recruited via Amazon MTurk. See Table \@ref(tab:demo) for a summary of participant characteristics. After data cleaning, `r nrow(climate)` participants were included in this study.

```{r demo, results='asis', warning=FALSE}
## climate_demo.csv is generated by create_tables.R

tab <- read_csv(here("manuscripts", "climate_demo.csv"))

names(tab)[1] <- "Demographic Characteristic"

Variables<-as.list(c(4:10, 12:19, 21:33))

papaja::apa_table(tab, caption="Demographic characteristics by study", stub_indents = Variables, longtable = TRUE)
```

## Material

## Procedure

## Data analysis
We used `r cite_r("manuscripts/r-references.bib")` for all our analyses.


# Results

```{r severity_int}

test <-  filter(climate, condition =="Control" | condition == "Severity")
t_out <- t.test(test$cc_int ~ as.factor(test$condition))

sev_tidy<-tidy(t_out)

sev<-apa_print(t_out)

```

```{r susceptibility_int}

test <-  filter(climate, condition =="Control" | condition == "Susceptibility")
t_out <- t.test(test$cc_int ~ as.factor(test$condition))

sus_tidy<-tidy(t_out)

sus<-apa_print(t_out)

```

```{r mrr_int}

test <-  filter(climate, condition =="Control" | condition == "Maladpative Response Rewards")
t_out <- t.test(test$cc_int ~ as.factor(test$condition))

mrr_tidy<-tidy(t_out)

mrr<-apa_print(t_out)

```

```{r se_int}

test <-  filter(climate, condition =="Control" | condition == "Self-Efficacy")
t_out <- t.test(test$cc_int ~ as.factor(test$condition))

se_tidy<-tidy(t_out)

se<-apa_print(t_out)

```

```{r re_int}

test <-  filter(climate, condition =="Control" | condition == "Response Efficacy")
t_out <- t.test(test$cc_int ~ as.factor(test$condition))

re_tidy<-tidy(t_out)

re<-apa_print(t_out)

```

```{r rc_int}

test <-  filter(climate, condition =="Control" | condition == "Response Costs")
t_out <- t.test(test$cc_int ~ as.factor(test$condition))

rc_tidy<-tidy(t_out)

rc<-apa_print(t_out)

```

A series of t-tests (see Table \@ref(tab:int)) were conducted to investigate the impact of each message on intention to vaccinate relative control. Messages designed to increase self-efficacy (`r se$statistic`) and response efficacy (`r re$statistic`) were effective, although other messages were not (Severity: `r sev$statistic`; Susceptibility: `r sus$statistic`; MRR: `r mrr$statistic`; Response Costs: `r rc$statistic`).

```{r int, results="asis"}
int_tidy<-rbind(sev_tidy, sus_tidy, mrr_tidy, se_tidy, re_tidy, rc_tidy)

int_tidy$comparisons <- c("Severity vs. Control", "Susceptibility vs. Control", "MRR vs. Control", "Self-efficacy vs. Control", "Response Efficacy vs. Control", "Response Costs vs. Control")

int_tidy$p.value <- printp(int_tidy$p.value)

int_tidy <- int_tidy %>% 
  select(comparisons, estimate1, estimate2, statistic, p.value)

apa_table(int_tidy, caption = "Impact of interventions on intention to vaccinate", placement = "htb", col.names=c("Comparisions", "Control Mean", "Intervention Mean", "\\textit{t}", "\\textit{p}"), align="lcccc")
```




```{r severity_coi}

test <-  filter(climate, condition =="Control" | condition == "Severity")
t_out <- t.test(test$cc_sev ~ as.factor(test$condition))

sev_tidy<-tidy(t_out)

sev<-apa_print(t_out)

```

```{r susceptibility_coi}

test <-  filter(climate, condition =="Control" | condition == "Susceptibility")
t_out <- t.test(test$cc_sus ~ as.factor(test$condition))

sus_tidy<-tidy(t_out)

sus<-apa_print(t_out)

```

```{r mrr_coi}

test <-  filter(climate, condition =="Control" | condition == "Maladpative Response Rewards")
t_out <- t.test(test$cc_mrr ~ as.factor(test$condition))

mrr_tidy<-tidy(t_out)

mrr<-apa_print(t_out)

```

```{r se_coi}

test <-  filter(climate, condition =="Control" | condition == "Self-Efficacy")
t_out <- t.test(test$cc_se ~ as.factor(test$condition))

se_tidy<-tidy(t_out)

se<-apa_print(t_out)

```

```{r re_coi}

test <-  filter(climate, condition =="Control" | condition == "Response Efficacy")
t_out <- t.test(test$cc_re ~ as.factor(test$condition))

re_tidy<-tidy(t_out)

re<-apa_print(t_out)

```

```{r rc_coi}

test <-  filter(climate, condition =="Control" | condition == "Response Costs")
t_out <- t.test(test$cc_rc ~ as.factor(test$condition))

rc_tidy<-tidy(t_out)

rc<-apa_print(t_out)

```

```{r coi, results="asis"}
coi_tidy<-rbind(sev_tidy, sus_tidy, mrr_tidy, se_tidy, re_tidy, rc_tidy)

#int_tidy<-cbind(c("Severity vs. Control", "Susceptibility vs. Control", "MRR vs. Control", "Self-efficacy vs. Control", "Response Efficacy vs. Control", "Response Costs vs. Control"), int_tidy)

coi_tidy$comparisons <- c("Severity vs. Control", "Susceptibility vs. Control", "MRR vs. Control", "Self-efficacy vs. Control", "Response Efficacy vs. Control", "Response Costs vs. Control")

coi_tidy$construct <- c("Severity", "Susceptibility", "MRR", "Self-efficacy", "Response Efficacy", "Response Costs")

coi_tidy$p.value <- printp(coi_tidy$p.value)

coi_tidy <- coi_tidy %>% 
  select(comparisons, construct, estimate1, estimate2, statistic, p.value)

apa_table(coi_tidy, caption = "Impact of interventions on target construct", placement = "htb", col.names=c("Comparisions", "Construct", "Control Mean", "Intervention Mean", "\\textit{t}", "\\textit{p}"), align="lcccc")
```


T-tests were also conducted to investigate the impact of each message on the PMT construct it was designed to target (i.e. the effect of the *self-efficacy* message on *self-efficacy*) relative to control. As shown in Table \@ref(tab:coi), only the self-efficacy message was successful in bringing about change in the the construct it was designed to target. 

## Exploratory analyses

In order to examine the potential pathway through which the Response Efficacy message leads to change in behaviour, an exploratory analysis was conducted to examine whether the Response Efficacy group differed from the Control group on any construct other than Response Efficacy and Intention.

```{r re_explor, results="asis"}

test <-  filter(climate, condition =="Control" | condition == "Response Efficacy")
t_out_sev <- t.test(test$cc_sev ~ as.factor(test$condition))
t_out_sus <- t.test(test$cc_sus ~ as.factor(test$condition))
t_out_mrr <- t.test(test$cc_mrr ~ as.factor(test$condition))
t_out_se <- t.test(test$cc_se ~ as.factor(test$condition))
t_out_rc <- t.test(test$cc_rc ~ as.factor(test$condition))

re_tidy<-rbind(tidy(t_out_sev), tidy(t_out_sus), tidy(t_out_mrr), tidy(t_out_se), tidy(t_out_rc))

re_tidy$construct <- c("Severity", "Susceptibility", "MRR", "Self-efficacy", "Response Costs")

re_tidy$p.value <- printp(re_tidy$p.value)

re_tidy <- re_tidy %>% 
  select(construct, estimate1, estimate2, statistic, p.value)

apa_table(re_tidy, caption="Exploratory analysis: impact of response efficacy message on other constructs", placement = "htb", col.names=c("Construct", "Control Mean", "Intervention Mean", "\\textit{t}", "\\textit{p}"), align="lcccc")

```


# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "manuscripts/r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
