---
title             : "HATCH Phase 2 - Draft Report"
shorttitle        : "Draft Report"

author: 
  - name          : "Emily Kothe"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : ""
    email         : "emily.kothe@deakin.edu.au"
  - name          : "Mathew Ling"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Deakin University"

author_note: |


abstract: |
  This is the draft report for HATCH Phase 2 Data
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
library("papaja")
library("readr")
library("dplyr")
```

```{r echo=FALSE, results='asis'}
options(knitr.kable.NA = '')
```


```{r}
dat <- read_rds("dat.rds")

flu <- dat %>% 
  filter(study=="Flu vaccination")

climate <- dat %>% 
  filter(study=="Climate Change")
```


# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

Participants were recruited via Amazon MTurk. See Table \@ref(tab:demo) for a summary of participant characteristics. After data cleaning, `r nrow(climate)` participants were included in the Climate Change study and `r nrow(flu)` in the Flu Vaccination study.

```{r demo, results='asis', warning=FALSE}
library(readr)
tab <- read_csv("demo.csv")

names(tab)[1] <- "Demographic Characteristic"

Variables<-as.list(c(4:10, 12:19, 21:33))

papaja::apa_table(tab, caption="Demographic characteristics by study", stub_indents= Variables, longtable = TRUE)
```

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
